Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-14 draft.Rmd
Update draft.Rmd

We offer a parallel case study of two longitudinal

>>>>

We our approach is a parallel case study  which uses two longitudinal panels, the British Household Pnael Survey, and the German Socio-Economic Panel. It has three strengths. First, we include firm internal mobility into our analysis of mobility types. Second, take a longitudinal approach to estimating the effects of changing jobs. In this way, we avoid the conclusions of authors who compare movers to non-movers; instead we are able to observe the effects of moving from one position to another. Third, we compare and contrast the effects of moving in two different institutional settings, where authors typically rely on one.

We offer two findings. First, quits and promotions have significantly different effects on earnings growth, depsite both commonly labeled as "voluntary". Internal promotions yield higher pay for workers in both countries. Quits have a minor effect, which are largely explained by changes in working hours. Second, the effect of promotions is larger in Germany than in the UK. This suggests the premium tied to promotion is greater in Germany. This high premium may act as an incentive to commit to the firm instead of the market, hence the lower rate of mobility among German workers. The minor effect of internal promotion
